Quantifying the ease of viral escape from broad and narrow antibodies to influenza hemagglutinin

### 2017-10-12 paper/manuscript.tex
completed legend for corr figure

\clearpage

@@

\clearpage

\small
\subsection*{ACKNOWLEDGMENTS}
This work was supported by grants R01GM102198 and R01AI127893 from the NIGMS and NIAID of the NIH.
MBD was supported in part by training grant T32AI083203 from the NIAID of the NIH.
JML was supported in part by \comment{CIDID grant}.
The research of JDB is supported in part by a Faculty Scholar Grant from the Howard Hughes Medical Institute and the Simons Foundation.

@@

\begin{suppfigure}
\centerline{\includegraphics[width=\textwidth]{figs/corrs/site_correlations.pdf}}
\caption{\label{suppfig:corr}
Correlation of measurements across replicates. 
Each point represents one site in HA, and gives the fraction of mutant virions surviving selection taken across all amino-acid mutations at that site.
\comment{Elaborate after writing formula in METHODS.}
}
\end{suppfigure}

>>>>

\clearpage
\small

@@

\subsection*{ACKNOWLEDGMENTS}
This work was supported by grants R01GM102198 and R01AI127893 from the NIGMS and NIAID of the NIH.
MBD was supported in part by training grant T32AI083203 from the NIAID of the NIH.
JML was supported in part by \comment{CIDID grant}.
The research of JDB is supported in part by a Faculty Scholar Grant from the Howard Hughes Medical Institute and the Simons Foundation.

@@

\begin{suppfigure}
\centerline{\includegraphics[width=0.84\textwidth]{figs/corrs/site_correlations.pdf}}
\caption{\label{suppfig:corr}
Correlations across experimental replicates. 
Each point represents one site in HA, and gives the fraction surviving above average across all amino-acid mutations at that site, as in Equation~\ref{eq:avgfracsurvive}.
The replicates are highly correlated for antibodies with strong escape mutations (S139/1, H17-L19, H17-L10, and H17-L7), and reasonably correlated for antibodies with only weak escape mutations (FI6v3 and C179).
}
\end{suppfigure}
